Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-25 Articles/ERK/erk.tex
ERK conclusion, abstract

\begin{abstract}{Abstract}
\todocomment{ADD}
\end{abstract}

@@

\todocomment{IMAGE OF THE TASK}

@@

The primary strength of this method is its ability to swiftly calculate directional guidance for the robot arm in real-time. By using a voxel grid, we can efficiently represent the 3D environment, and the use of 3D directional kernels allows for robust calculations of obstacle proximity and directions of free space. This is beneficial in dynamic environments where quick responses are required. Moreover, this approach does not require extensive training as with neural networks, making it easier to deploy in new environments.

@@

%\[
%v = \sum_{x}\sum_{y}\sum_{z} a_{xyz} ~c_{xyz}
%\]

@@

\todocomment{ADD}

>>>>

\begin{abstract}{Abstract}

This study proposes a method for real-time obstacle avoidance in robotic arm control, leveraging a 3D voxel grid and 3D directional kernels. The approach integrates the benefits of convolutional techniques with the spatial understanding provided by voxel grid representation to efficiently calculate movement directions while evading obstacles. By focusing on kinematics and obstacle grid representation, the method efficiently utilizes the versatility of a 7-degree-of-freedom (DOF) robot arm, employing geometric and differential kinematics for movement calculations. The strategy doesn't require exhaustive training as with neural networks, making it deployable in various environments.

\end{abstract}

@@

@@

The primary strength of the proposed method is its ability to swiftly calculate directional guidance for the robot arm in real-time. By using a voxel grid, we can efficiently represent the 3D environment, and the use of 3D directional kernels allows for robust calculations of obstacle proximity and directions of free space. This is beneficial in dynamic environments where quick responses are required. Moreover, this approach does not require extensive training as with neural networks, making it easier to deploy in new environments.

@@

@@

%This paper presented a novel approach to robotic motion planning, combining the application of kernel convolution for obstacle avoidance velocity calculations with an integration of attractive and repulsive field velocities for end-effector trajectory generation and robot joint obstacle avoidance. The method was validated using the kinematic model of a 7 DoF Panda Emika robot, demonstrating its operational versatility and adaptability in varying workspace conditions.
%
%Notable advantages of our approach include its simplicity and the fact that we work directly in the obstacle space grid, negating the necessity for calculating the spatial primitives of shapes. Moreover, when implemented in parallel, our method exhibits high computational efficiency, making it a viable solution for real-time applications. The experiments conducted effectively showcased that the end-effector could move efficiently towards the target while successfully avoiding obstacles, specifically, a wall in this instance.
%
%Our results affirmed the robustness of the proposed approach, as evidenced by the robot's fourth joint being approximately 20 cm further from the wall upon task completion when the avoidance algorithm was employed.
%
%Despite the promising initial results, our approach does present some limitations. Particularly, the possibility of encountering local minima traps poses a significant challenge. Although these traps could be potentially mitigated by incorporating multiple convolutional kernels of varying sizes, it would result in an approach similar to convolutional neural networks (CNNs), adding to the complexity and computational cost of the algorithm.
%
%Additionally, we acknowledge that our study was conducted under simplified conditions with a single type of obstacle. As such, future work should focus on validating the proposed method in more complex environments, with different obstacle types, shapes, and densities, to further ascertain its adaptability and robustness. It may also be beneficial to explore the integration of other optimization strategies and machine learning techniques to further enhance the overall efficiency and effectiveness of the trajectory planning process.
%
%In conclusion, our work serves as a solid foundation for the development of more advanced and dynamic motion planning algorithms.

This paper presented a novel approach to robotic motion planning, combining the application of kernel convolution for obstacle avoidance velocity calculations with an integration of attractive and repulsive field velocities for end-effector trajectory generation and robot joint obstacle avoidance. The method was validated using the kinematic model of a 7 DoF Panda Emika robot, demonstrating its operational versatility and adaptability in varying workspace conditions.

Notable advantages of our approach include its simplicity and the fact that we work directly in the obstacle space grid, negating the necessity for calculating the spatial primitives of shapes. Moreover, when implemented in parallel, our method exhibits high computational efficiency, making it a viable solution for real-time applications. The experiments conducted effectively showcased that the end-effector could move efficiently towards the target while successfully avoiding obstacles, specifically, a wall in this instance.

Our results affirmed the robustness of the proposed approach, as evidenced by the robot's fourth joint being approximately 20 cm further from the wall upon task completion when the avoidance algorithm was employed.

Despite its effectiveness, the approach could potentially fall into local minima traps. This limitation could be addressed by incorporating multiple convolutional kernels, though this would increase complexity and resemble convolutional neural networks.

Additionally, we acknowledge that our study was conducted under simplified conditions with a single type of obstacle. As such, future work should focus on validating the proposed method in more complex environments, with different obstacle types, shapes, and densities, to further ascertain its adaptability and robustness. It may also be beneficial to explore the integration of other optimization strategies and machine learning techniques to further enhance the overall efficiency and effectiveness of the trajectory planning process.
